Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-11 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:11	11:37:35	(Tue11.Aug)

\IEEEPARstart{T}{he} best adaptive sonars are found in nature. Bats, for instance, use a high frequency sonar to detect, identify and track prey with amazing precision in caves amongst a myriad of other bats. In comparison, most human made active sonars inhibit a static behaviour when they collect data, but

\IEEEPARstart{A}{daptive} methods detector design is a term methods have been introduced in various imaging fields over the years in attempts to improve image quality. One such method is the minimum variance distortionless response (MVDR) beamformer. Compared to conventional methods, MVDR is often able to improve image contrast and resolution, as shown in~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}.

>>>>

\IEEEPARstart{T}{he} best adaptive sonars are found in nature. Bats, for instance, use a high frequency sonar to detect, identify and track prey with amazing precision in caves amongst a myriad of other bats. In comparison, human made sonars inhibit minimal adaptability in the data collection process, but try to make up for it in the post processing of the data. Perhaps the most studied adaptive method for reconstructing a sonar image is the minimum variance distortionless response (MVDR) beamformer.

Compared to conventional methods, MVDR is often able to improve image contrast and resolution, as shown in~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}.
